---
title: "Hello, Penguins!"
format: revealjs
---

## Data

For this analysis we'll use the penguins dataset from the palmerpenguins package. First I'll use the `tidyverse` library. Then I'll use the `ggthemes` library.


```{r}
#| label: load-packages
#| message: false

library(tidyverse)
library(ggthemes)
library(palmerpenguins)
library(gt)
```


## Species

The figure below is a bar plot of species of penguins. The species are:

1. Adelie
2. Gentoo
3. Chinstrap

```{r}
ggplot(
  penguins,
  aes(
    x = bill_length_mm, y = bill_depth_mm,
    color = species, shape = species
  )
) +
  geom_point() +
  scale_color_colorblind() +
  labs(x = "Bill length (mm)", y = "Bill depth (mm)") +
  theme_minimal()
```

# Data Tables

## Penguins

The table below shows the first 10 penguins from the dataset.

```{r}
penguins |>
  slice_head(n = 10)
```

## Penguins

The table below shows the first 10 penguins from the dataset.

```{r}
penguins |>
  slice_head(n = 10) |>
  select(species, island, bill_length_mm, bill_depth_mm) |>
  gt()
```
