---
title: "Hello, Penguins!"
format:
  revealjs:
    logo: "images/quarto-logo.png"
    footer: "All about Penguins"
---

## Data

For this analysis we'll use the penguins dataset from the palmerpenguins package. [First I'll use the `tidyverse` library]{.fragment .highlight-red}. Then I'll use the `ggthemes` library.

. . .

For this analysis we'll use the penguins dataset from the palmerpenguins package. [First I'll use the `tidyverse` library]{.fragment .highlight-red}. Then I'll use the `ggthemes` library.


```{r}
#| label: load-packages
#| message: false

library(tidyverse)
library(ggthemes)
library(palmerpenguins)
library(gt)
```

:::{.notes}
Remind folks to install packages before loading.
:::

## Species {.smaller auto-animate=TRUE}

:::{.columns}

:::{.column width="40%"}

The figure below is a bar plot of species of penguins. The species are:

1. Adelie
2. Gentoo
3. Chinstrap

:::

:::{.column width="60%"}

other stuff

```{r}
#| label: bill-dims-species2
#| warning: false
#| fig-width: 5
#| fig-asp: 0.618

ggplot(
  penguins,
  aes(
    x = bill_length_mm, y = bill_depth_mm,
    color = species, shape = species
  )
) +
  geom_point() +
  scale_color_colorblind() +
  labs(x = "Bill length (mm)", y = "Bill depth (mm)") +
  theme_minimal()
```

:::

:::

## Species {.smaller auto-animate=TRUE}

:::{.columns}

:::{.column width="40%"}

1. Chinstrap
2. Gentoo
3. Adelie

The figure below is a bar plot of species of penguins. The species are:

:::

:::{.column width="60%"}

other stuff

```{r}
#| label: bill-dims-species
#| warning: false
#| fig-width: 5
#| fig-asp: 0.618

ggplot(
  penguins,
  aes(
    x = bill_length_mm, y = bill_depth_mm,
    color = species, shape = species
  )
) +
  geom_point() +
  scale_color_colorblind() +
  labs(x = "Bill length (mm)", y = "Bill depth (mm)") +
  theme_minimal()
```

:::

:::

# Data Tables

## Penguins {auto-animate=TRUE}

The table below shows the first 10 penguins from the dataset.

```{r}
#| label: penguins-top10
#| echo: true

penguins |>
  slice_head(n = 10)
```

## Penguins {auto-animate=TRUE}

The table below shows the first 10 penguins from the dataset.

```{r}
#| label: penguins-top10b
#| echo: true

penguins |>
  slice_head(n = 10) |>
  select(species, island, bill_length_mm, bill_depth_mm) |>
  gt()
```
